EinsteinPy: Python for General Relativity\footnote{Released on July, 15th, 2019}

### 2020-01-20 paper.tex

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.3
\documentclass{aastex63}

@@

\section{INFRASTRUCTURE} \label{sec:INFRASTRUCTURE}
\subsection{ Testing} \label{subsec: Testing}
The EinsteinPy Project maintains a very high bar in accepting changes and introducing new features. Every patch of code that is accepted in the codebase through any pull request has to be well tested using some unit tests unless given an exception after discussion with both the lead developers. Currently the coverage of unit tests, which means the total fraction of codebase run by at least one unit test is 94% and we hope to improve it in the future. The 100% code coverage for this software at this level is not possible because of lack of accurate data to test the code against. We deliberately leave some parts of the codebase out of the testing loop because testing those modules is not possible with the current knowledge level and expertise. However, 94% code coverage is good enough when we consider other packages in scientific Python community who face the similar problem.

>>>>

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.3
\documentclass{aastex63}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}

@@

\section{The EinsteinPy Core Package}
This section explains in detail, the modules available within EinsteinPy core pacakge, their API and the purpose they serve.
\subsection{METRIC}
This module captures all the geometric and causal structure of specific spacetimes, and being able to calculate trajectories in a given space-time. 
The module derives its name from Metric Tensor, a tensorial quantity used to describe differential lengths, especially in a curved space-time. 
However, this module serves more than its usual definition and ultimately leads us to obtain geodesics of particles in a spacetime with high curvature, where notions of newtonian physics fail.
\subsubsection{Schwarzschild Metric}
Karl Schwarzchild pioneered the analysis of the relation between the size of black hole and its mass and this work paved the way for the first exact solution of Einstein's Field Equation under the limited case of single spherical non-rotating, non-charged body. 
The metric equation corrosponding to a space-time centred around a body in the above described conditions is given by,

\begin{align}
& ds^2 = -d\tau ^2 = - (1 - \frac{r_s}{r})c^2 dt^2  + \frac{1}{(1 - \frac{r_s}{r})}dr^2 + r^2 d\theta ^2 + r^2 sin^2 \theta d\phi ^2
\end{align}

The same equation can be written in a tensorial form as follows,

\begin{gather}
g_{\mu \nu} = \begin{bmatrix} - (1 - \frac{r_s}{r})c^2 & 0 & 0 & 0 \\ 0 & \frac{1}{(1 - \frac{r_s}{r})} & 0 & 0 \\ 0 & 0 & r^2 & 0 \\ 0 & 0 & 0 &  r^2 sin^2 \theta \end{bmatrix} \\ 
\nonumber \\
ds^2 = g_{\mu \nu} dx^\mu dx^\nu
\end{gather}

where $r_s$ is the schwarzschild radius of a given heavy body and is given by the equation,

\begin{gather}
r_s = \frac{2GM}{c^2}
\end{gather}

$G$, $M$, and $c$ are gravitational constant, mass of the body and speed of light in vacuum respectively.

\subsubsection{Kerr Metric}
\subsubsection{Kerr-Newman Metric}

\subsection{COORDINATES}
\subsection{SYMBOLIC}
\subsection{HYPERSURFACE}
\subsection{PLOTTING}

\section{INFRASTRUCTURE} \label{sec:INFRASTRUCTURE}
\subsection{ Testing} \label{subsec: Testing}
The EinsteinPy Project maintains a very high bar in accepting changes and introducing new features. Every patch of code that is accepted in the codebase through any pull request has to be well tested using some unit tests unless given an exception after discussion with both the lead developers. Currently the coverage of unit tests, which means the total fraction of codebase run by at least one unit test is 94\% and we hope to improve it in the future. The 100\% code coverage for this software at this level is not possible because of lack of accurate data to test the code against. We deliberately leave some parts of the codebase out of the testing loop because testing those modules is not possible with the current knowledge level and expertise. However, 94\% code coverage is good enough when we consider other packages in scientific Python community who face the similar problem.
